Model Search in Relational Domains

### 2016-10-23 experiments.tex
nudge

We have implemented the instantiation of ACDCL on relational domains in the
2LS verification tool~\cite{2ls}.  We have used the abstract domains
provided by 2LS (intervals, octagons, polyhedra and equalities) for our
experiments.  The performance of the abstract domain implementations in 2LS
is not competitive with that of the APRON~\cite{apron} library; however, the
domain implementation in 2LS handles all C operators (including bitwise
operations) and supports precise complementation of meet irreducibles, which
is necessary for conflict-driven learning.  Our tool and benchmarks are
available online\footnote{http://www.cprover.org/acdcl/} to enable other
researchers to reproduce our results.

>>>>

We have implemented the instantiation of ACDCL on relational domains in the
2LS verification tool~\cite{2ls}.  We have used the abstract domains
provided by 2LS (intervals, octagons, polyhedra and equalities) for our
experiments.  The performance of the abstract domain implementations in 2LS
is not competitive with that of the APRON~\cite{apron} library; however, the
domain implementation in 2LS handles all C operators (including bit-wise
operations) and supports precise complementation of meet irreducibles, which
is necessary for conflict-driven learning.  Our tool and benchmarks are
available online\footnote{http://www.cprover.org/acdcl/} to enable other
researchers to reproduce our results.
